Finding Optimal Sequences for Area Aggregation---\protect\\ \Astar vs. Integer Linear Programming

### 2020-07-13 area_agg_seq_tsas.tex
polished the paper

\begin{document}
\title
[Finding Optimal Sequences for Area Aggregation] %short title
{Finding Optimal Sequences for Area Aggregation---\\
  \texorpdfstring
    {\Astar vs.\ Integer Linear Programming}%title of the paper
    {A* vs.\ Integer Linear Programming}%title of the pdf
}

@@

\author{Dongliang Peng}
%\authornote{Dr.~Trovato insisted his name be first.}
\orcid{0000-0001-6848-3545}
\affiliation{%
  \institution{GIS Technology, 
  	Delft University of Technology}
%  \streetaddress{P.O. Box 1212}
%  \city{Dublin}
%  \state{Ohio}
%  \postcode{43017-6221}
  \country{The Netherlands}
}
\affiliation{%
  \institution{Chair of Computer Science I, 
  	University of W\"urzburg}
%  \streetaddress{P.O. Box 1212}
%  \city{Dublin}
%  \state{Ohio}
%  \postcode{43017-6221}
  \country{Germany}
}
\email{http://www.gdmc.nl/staff/}

\author{Alexander Wolff}
\orcid{0000-0001-5872-718X}
\affiliation{%
  \institution{Chair of Computer Science I, 
  	University of W\"urzburg}
  \country{Germany}
}
\email{www1.informatik.uni-wuerzburg.de/wolff}

\author{Jan-Henrik Haunert}
\orcid{0000-0001-8005-943X}
\affiliation{%
  \institution{Institute of Geodesy and Geoinformation,  
  University of Bonn}
  \country{Germany}
}
\email{www.geoinfo.uni-bonn.de/haunert}

@@

\keywords{Continuous map generalization, Land cover, 
	 Type change, Compactness, Shortest path
%	 , Optimization, Exponential, NP-hard
	 }

@@

In our digital age, people interactively read maps 
on computers and mobile phones.
An often used interaction is zooming. 
When users zoom in or out, 
a map must be changed to provide information 
appropriate to the corresponding zoom level.
However, large discrete changes may distract users.
The \emph{on-the-fly generalization}~\parencite{Weibel2017Fly},
which generalizes map features (e.g., polyglines and polygons) 
in real time, can mitigate this problem.
Still, large discrete changes can be introduced.
By a usability test, \textcite{Midtbo2007} have shown that 
a map is easier to follow 
if the map extent transits smoothly than stepwise. 
In addition to smoothly transiting map extent, 
we want to change also map features smoothly 
when users are zooming.
We believe that this strategy will allow users 
to follow maps even more easily.
The process of producing maps \mine{with a smooth scale transition}
is known as \emph{continuous map generalization} (CMG), 
or simply \emph{continuous generalization}.
Ideally, there should be no discrete change in CMG.
However, the term is also used when 
the discrete changes are small enough not to be noticed as,
e.g., \textcite{Suba2016Road} stated.
%We consider CMG as the process of producing maps 
%covering a continuous interval of scales,
%where CMG considers constraints and quality measures 
%that act across different scales. 
%In our work, for example, the quality of an aggregation sequence 
%is measured as a whole; 
%whereas in classical generalization approaches, 
%only the quality of a map at \mine{an} output scale is measured.
%We consider CMG possible, desirable, and realistic.
%In CMG, it is not necessary that 
%all changes that occur during zooming are animated in a continuous fashion. 
%That fashion may generally be possible.

@@

A \emph{land-cover map} is a planar subdivision in which 
each area belongs to a land-cover class or \emph{type}.
Suppose that there are two land-cover maps of different scales 
that cover the same spatial region.
We consider the problem of finding a sequence 
of small incremental changes that gradually transforms 
the larger-scale map (the \emph{start map}) to 
the smaller-scale map (the \emph{goal map}).
We use this sequence to generate and show land-cover maps at 
intermediate scales (see \fig\ref{fig:AreaAgg_example}).
In this way, we try to avoid large and discrete changes
during zooming.

@@

With the same motivation, 
a strategy of hierarchical schemes has been proposed.
This strategy generalizes a more-detailed representation 
to obtain a less-detailed representation 
based on small incremental changes, 
e.g., the Generalized Area Partitioning tree (GAP-tree).
This tree can be constructed if only the larger-scale map is given
\citep{vanOosterom2005} 
or if both the larger-scale map and the smaller-scale map 
are given \citep{HaunertDilo2009}.
Typically, the next change in such a sequence 
is determined locally, in a greedy fashion.  
If we insist on finding a sequence that is optimal 
according to some global measure,
the problem becomes complicated.

We assume that there exist many-to-one relationships 
between the areas of the start map and the areas of the goal map.
This assumption is based on the fact that many algorithms 
\parencite[e.g.,][]{HaunertWolff2010AreaAgg,
vanSmaalen2003,Oehrlein2017Aggregation}
result in many-to-one relationships
when aggregating land-cover areas.
Their inputs and generalized results together
can be used as our inputs.
However, we should not use those algorithms
to generate a sequence of maps at different scales
because those algorithms do not take into account 
the consistence between the generated maps.
We use both a start map and a goal map instead of using only the start map
because our generated maps at intermediate scales should be able to
benefit from a goal map with high quality.

We term the areas of the goal map \emph{regions}.
That is, every region is the union of a set of areas 
on the start map.
The type of a region may differ from the types of its components. 
For example, a small water area together with 
multiple adjacent forest areas may constitute 
a large forest region on the \mine{goal} map.
However, we assume that every region, on the goal map, 
contains at least one area of the same type on the start map.
Our assumptions hold if the goal map has been produced 
with an automatic method for area aggregation, 
for example, by the method of \citet{HaunertWolff2010AreaAgg}.
That method produces a land-cover map at a single smaller scale, 
given a land-cover map at a larger scale.
Although \textcite{HaunertWolff2010AreaAgg}
attain results of high quality, 
they do not produce a sequence of maps.

Our method can also be extended to find an aggregation sequence 
for two maps (a start map and a goal map) that are from different sources.
In that case, one could compute a map overlay of the two maps
and use the result 
(with combined boundaries from both input maps and land cover classes 
from the given larger-scale map) 
as the start map.

In this paper, we try to find an optimal sequence
to aggregate the land-cover areas on the start map
one by one until we arrive at the goal map.
We first independently deal with each region of the goal map 
(with its components on the start map).
Once we have found an aggregation sequence for each region, 
we integrate all the sequences into an overall sequence,
which transforms the start map into the goal map
(see \fig\ref{fig:AreaAgg_IntegrateSequence}). 
Our aggregation sequence may be cooperated with
the GAP-face tree \citep{vanOosterom2005},
the map cube model \citep{Timpf1998},
or ScaleMaster \citep{Brewer2007Guidelines,Touya2013ScaleMaster}, 
to support on-the-fly visualization.
Smoothly (dis-)appearing areas can be realized
by integrating our results into the \emph{space-scale cube}
\parencite{vanOosterom2014Support,vanOosterom2014tGAPSSC}.

\begin{figure*}[tb]
\centering
\includegraphics[page=2]{AreaAgg_Preliminaries}
\caption{Integrating two aggregation sequences 
	of different regions: 
	the resulting sequence contains the given sequences 
	as subsequences and 
	always takes the subdivision with smallest patch next.
	The gray arrows show the integration of the two regions.
}
\label{fig:AreaAgg_IntegrateSequence}
\end{figure*}

\mypar{Contribution}
We \mine{first} show \mine{some} related work (\sect\ref{sec:AreaAgg_RelatedWork}).
Then, we formally model our problem, 
analyze the size of our model in a worst-case scenario,
introduce our methods,
and present the basic concepts of our method
(\sect\ref{sec:AreaAgg_Preliminaries}).
We define our cost functions 
(\sect\ref{sec:AreaAgg_CostFunctions}).
We prove that our problem is NP-hard
(\sect\ref{sec:AreaAgg_NP-hardness}).
Then, we develop and compare three methods 
for finding aggregation sequences.
First, we present 
a greedy algorithm (\sect\ref{sec:AreaAgg_Greedy}).
Second, we develop a new global optimization approach
based on the \Astar algorithm 
(\sect\ref{sec:AreaAgg_AStar}).
Third, we model our pathfinding problem as
an \emph{integer linear program} (ILP), 
and we solve this ILP with minimizing our cost function
(\sect\ref{sec:AreaAgg_ILP}).
Our ILP uses binary (0--1) variables. 
These variables help us to model our problem, 
but in general, it is NP-hard 
to solve an ILP optimally.
By comparing with the greedy algorithm, 
which is used as a benchmark,
we are able to see whether \Astar or the ILP-based algorithm, 
which are more complex and slower, indeed perform better.  
Our case study 
uses a dataset of the German topographic database ATKIS 
(\sect\ref{sec:AreaAgg_CaseStudy}).
In the concluding remarks, we show possible ways to improve our 
methods (\sect\ref{sec:AreaAgg_Conclusions}).

We do not deal with simplifying polylines in this paper.
The simplification can be handled separately from the
aggregation of areas, for example, 
by using one method of 
\textcite{Douglas1973},
\textcite{Saalfeld1999},
or \textcite{Wu2004DP}.
Those methods can be used to set up 
the binary line generalisation tree (BLG-tree) of
\textcite{vanOosterom1995Development},
which is a hierarchical data structure that 
defines a gradual line simplification process.
\mine{Note that simplifying polylines will not speed up 
our three algorithms.
The reason is that we compute the areas of the polygons 
and the lengths of the boundaries in a preprocessing.
These values will be associated with
a graph representation of the dataset, 
where polygons are represented as vertices and 
a boundary separating two polygons (no matter how detailed it is) 
is represented with a single edge.
During computation, the three algorithms do not need to go through 
the vertices of the land-cover areas.
}

@@

\emph{Continuous map generalization} (CMG)
has received a lot of attention
from cartographers and computer scientists.
\Textcite{vanKreveld2001} proposed five gradual changes
to support the continuous zooming of maps, 
which are \emph{moving}, \emph{rotating}, \emph{morphing}, 
\emph{fading}, and \emph{appearing}. 
He suggested using these gradual changes 
to adapt discrete generalization operators for CMG.
\textcite{Sester2005_CG} suggested simplifying building
footprints based on small incremental steps and 
to animate each step smoothly.
\textcite{Li2012Continuous} built hierarchies of road segments,
which they then used to omit road segments 
from lower levels of the hierarchy.
Moreover, they evaluated similarities 
between their results and existing maps.
\textcite{Peng2017Building} gradually grew
buildings to built-up areas by aggregating buildings 
whenever they become too close.
\textcite{Touya2017Progressive} progressively replaced
buildings with blocks. 
In addition, their method automatically inferred landmarks 
and put the landmarks on top of the blocks.
\textcite{Suba2016Road} continuously generalized road networks
which are represented as a set of areas.
Their method repeatedly finds the least-important area 
and then either merges it with an adjacent area 
or collapses it to a line segment.
\textcite{Danciger2009} investigated the growing of regions, 
while preserving topology, area ratios, and
relative positions.
The strategy of using two maps at different scales
to generate intermediate-scale maps has been studied in multiple
representations, e.g., with respect to the selection of roads or
rivers~\parencite{Peng2012River,Girres2014}. 
Actually, this strategy is the key idea of the
morphing-based methods for CMG.
In order to morph from one polyline to another polyline,
which respectively represent, say, roads on a larger-scale map 
and a smaller-scale map, we first need to compute 
corresponding points between them 
\parencite[e.g.,][]{Cecconi2003,Noellenburg2008,Chazal2010BallMap,
Deng2015,Li2017_Building,Li2017Annealing}.
Then morphing can be realized by interpolating a set of 
intermediate polylines.
% Among the methods of computing corresponding points,
\textcite{Noellenburg2008} computed an optimum
correspondence between two given polylines 
according to some cost function.
While straight-line trajectories 
are often used for interpolation
\parencite[e.g.,][]{Cecconi2003,Deng2015},
\textcite{Whited2011BallMorph} considered four other alternatives, 
i.e., \emph{hat}, \emph{tangent}, \emph{circular}, 
and \emph{parabolic} paths
based on so-called \emph{ball-map}
\parencite{Chazal2010BallMap}.
\textcite{Peng2013LSA} defined trajectories requiring that
angles in vertices and edge lengths should change linearly.
As these requirements may not agree with each other,
their method mediates between them using 
least-squares adjustments.
\textcite{Peng2016Admin} morphed county boundaries
to provincial boundaries.
For county boundaries that do not have corresponding 
provincial boundaries, they generated the correspondences based 
on \emph{compatible triangulations}.
\Textcite{vanOosterom2014Support} used
a data structure called
\emph{smooth topological generalized area partitioning}
to support visualizing CMG.
One of their contributions is that
a polygon is merged into another polygon continuously
by moving the boundary of the former.
\textcite{Huang2017Matrix} proposed a matrix-based structure 
to support CMG,
using a river network as an example.
For a given scale, 
their structure yields the rivers that should be kept 
as well as how much these rivers should be simplified.

@@

Map generalization generally specifies 
and takes into account requirements
in order to produce maps of high quality
\parencite{Stoter2009Requirements}.
We categorize requirements as hard and soft constraints.
For example, when users zoom out, 
some land-cover areas become too small to be seen.
These areas need to be aggregated.
When we aggregate one area into another, 
the type of the former is changed to the type of the latter. 
In this problem, a hard constraint could be that 
we aggregate only two polygons at each step 
in order to keep changes small
(see for example \fig\ref{fig:AreaAgg_example}). 
A soft constraint could be that 
we wish to minimize the changes of types, e.g., 
we prefer aggregating a grass area into a farm area 
rather than into a settlement area.
This is a typical \emph{optimization} problem,
where we stick to hard constraints and 
try to fulfill soft ones as well as possible.
Optimization for map generalization is important 
not only because it finds optimal solutions,
but also because it helps us to evaluate the quality of a model
\parencite{Haunert2017Label,
Haunert2008Assuring,Haunert2016Optimization}.
When we wish to minimize the changes of types
in aggregating areas one by one,
a model could be to minimize 
the \emph{greatest} change over all the steps.
Using a greedy algorithm,
we can minimize the change at each step,
but the result does not necessarily minimize the greatest change
over all the steps.
If a result is bad,
we cannot tell if the bad result comes from the model 
or from the greedy algorithm.
Using optimization,
we are able to find optimal solutions
of the model at least for small instances.
If even an optimal solution is bad,
then we can exclude that the bad result 
is from the greedy algorithm.
That is to say,
the bad result is because of the model.
In this case, we should improve the model; 
we may want to minimize 
the \emph{average} change over all the steps.
Moreover, optimization is useful for evaluating heuristics.
We need heuristics because
many optimization problems cannot be solved efficiently
\parencite[e.g.,][]{HaunertWolff2010AreaAgg,Haunert2016Partition}.
While heuristics can find some solutions in reasonable time,
it is important to know the quality of 
these solutions.
Fortunately, we can often find an optimal solution when 
the size of an instance is sufficiently small.
Consequently, we are able to evaluate 
the quality of a heuristic 
by comparing its results with optimal solutions
on small instances.

Optimization has been widely used in map generalization.
For example, \textcite{Harrie1999} displaced objects 
based on least-squares adjustments (LSA)
to solve spatial conflicts.
In his problem, the soft constraints 
for shapes and locations may contradict each other.
Therefore, it is necessary 
to mediate between these constraints, 
which can be done by LSA.
\textcite{Sester2005Optimization} used LSA not only for 
displacing objects but also for simplifying buildings. 
She required that 
the output boundaries should be 
as close to the original buildings as possible.
\textcite{Tong2015AreaLSA} generalized land-cover areas,
where LSA was used to preserve the sizes of 
the land-cover areas.
\textcite{Regnauld2001} grouped buildings based on 
minimum spanning trees in order to typify
the buildings in a group.
\textcite{Burghardt2005Snakes} smoothed lines based on 
energy minimization. 
According to his setting, a line contains less energy
if it is smooth and close to the original line.
He repeatedly displaced the line 
until a stable state 
in terms of minimizing his energy function is found.
\textcite{HaunertWolff2010AreaAgg} aggregated land-cover areas
based on mixed-integer linear programming
to generate a map at a target scale.
Their method is based on a global optimization.
They minimize a combination of type changes and cost for non-compact shapes 
while satisfying constraints on the sizes of the output regions.
\textcite{Haunertwolff2010Building} simplified building
footprints by solving an integer linear program (ILP).
They aimed at minimizing the number of edges in the output 
under the restriction that 
the simplified buildings must be topologically safe,
that is, the selected and extended edges must not intersect with 
each other.
\textcite{Oehrlein2017Aggregation} aggregated the departments 
of France according to unemployment rates based on integer 
linear programming; they used a cutting-plane method to 
speed up solving their ILP.
\textcite{Funke2017Simplification} simplified 
administrative boundaries based on an ILP.
Their aim was to minimize the number of edges
while keeping the result boundaries close to the original ones
and avoiding any intersection. 
At the same time, they required that every city, 
represented by a point, 
stays in the same face as before the generalization.

@@

Optimization becomes more delicate
when we deal with CMG.
In this field, we have requirements 
not only for a specific map
but also for relations between maps at difference scales. 
%
Some optimization techniques have been applied to CMG.
In the aforementioned article,
\textcite{Noellenburg2008} used dynamic programming
to match points of two polylines to support morphing
according to some matching cost.
\textcite{sahw-oarps-ICAGW13} used 
mixed-integer linear programming 
to select points of interest.
They required that a point, once disappeared, 
should not show up again during zooming out. 
They also required that any two points should be 
sufficiently far away from each other.
Based on these requirements, 
they wanted to show as many points as possible 
for a given scale interval.
\textcite{Chimani2014Eat} computed a deletion sequence
for a road network by integer linear programming
and efficient approximation algorithms.
They wanted to delete a stroke, 
which is a sequence of edges, at each step
while keeping the remaining network connected.
They assigned each edge a weight, 
and their objective was to maximize the total weight 
over all the road networks of all the steps.
\textcite{Peng2013LSA} defined trajectories 
based on LSA for morphing between polylines, 
where LSA is used to mediate between the requirements 
for angles and edge lengths of the intermediate polylines.

@@

\begin{figure}[tb]
\centering
\includegraphics[page=2]{AreaAgg_NPHard}
\caption{The situation after Phase I has been conducted 
    such that all black vertices corresponding to a vertex cover 
    of~$G_\mathrm{A}$ have been recolored white.
    The dashed areas represent the vertices that are merged.}
\label{fig:reduction2}
\end{figure}
\end{proof}

@@

>>>>

\begin{document}
\title
[Finding Optimal Sequences for Area Aggregation] %short title
{Finding Optimal Sequences for Area Aggregation---\\
  \texorpdfstring
    {\Astar} %title of the paper
    {A*} %title of the pdf 
    vs.\ Integer Linear Programming
}

@@

\author{Dongliang Peng}
\authornote{Dongliang Peng did his main contribution 
when he was a PhD student at University of W\"urzburg.}
\orcid{0000-0001-6848-3545}
\affiliation{%
  \institution{GIS Technology, 
  	Delft University of Technology}
  \streetaddress{Julianalaan 134}
  \city{Delft}
  \state{South Holland}
  \postcode{2628 BL}
  \country{The Netherlands}
}
\email{http://www.gdmc.nl/staff/}
\affiliation{%
  \institution{Chair of Computer Science I, 
  	University of W\"urzburg}
  \streetaddress{Am Hubland}
  \city{W\"urzburg}
  \state{Bavaria}
  \postcode{D-97074}    
  \country{Germany}
}
\email{http://www1.informatik.uni-wuerzburg.de/peng}

\author{Alexander Wolff}
\orcid{0000-0001-5872-718X}
\affiliation{%
  \institution{Chair of Computer Science I, 
  	University of W\"urzburg}
  \streetaddress{Am Hubland}
  \city{W\"urzburg}
  \state{Bavaria}
  \postcode{D-97074}    
  \country{Germany}
}
\email{www1.informatik.uni-wuerzburg.de/wolff}

\author{Jan-Henrik Haunert}
\orcid{0000-0001-8005-943X}
\affiliation{%
  \institution{Institute of Geodesy and Geoinformation,  
  University of Bonn}
  \streetaddress{Meckenheimer Allee 172}
  \city{Bonn}
  \state{North Rhine-Westphalia}
  \postcode{D-53115}  
  \country{Germany}
}
\email{www.geoinfo.uni-bonn.de/haunert}

@@

\keywords{Continuous map generalization, Land-cover area, 
	 Type change, Compactness, Shortest path
%	 , Optimization, Exponential, NP-hard
	 }

@@

In our digital age, people interactively read maps 
on computers and mobile phones.
An often used interaction is zooming. 
When users zoom in or out, 
a map must be changed to provide information 
appropriate to the corresponding zoom level.
However, large discrete changes may distract users.
The \emph{on-the-fly generalization}~\parencite{Weibel2017Fly},
which generalizes map features (e.g., polylines and polygons) 
in real time, can mitigate this problem.
Still, large discrete changes can be introduced.
By a usability test, \textcite{Midtbo2007} have shown that 
a map is easier to follow 
if the map extent changes smoothly than stepwise. 
In addition to smoothly changing map extent, 
we want to change also map features smoothly 
when users are zooming.
We believe that this strategy will allow users 
to follow maps even more easily and thus keep their context better.
The process of producing maps \mine{with a smooth scale transition}
is known as \emph{continuous map generalization} (CMG), 
or simply \emph{continuous generalization}.
Ideally, there should be no discrete change in CMG.
However, the term is also used when 
the discrete changes are small enough not to be noticed
\parencite[e.g.,][]{Suba2016Road}.
% as,
%e.g., \textcite{Suba2016Road} stated.
%We consider CMG as the process of producing maps 
%covering a continuous interval of scales,
%where CMG considers constraints and quality measures 
%that act across different scales. 
%In our work, for example, the quality of an aggregation sequence 
%is measured as a whole; 
%whereas in classical generalization approaches, 
%only the quality of a map at \mine{an} output scale is measured.
%We consider CMG possible, desirable, and realistic.
%In CMG, it is not necessary that 
%all changes that occur during zooming are animated in a continuous fashion. 
%That fashion may generally be possible.

@@

A \emph{land-cover map} is a planar subdivision in which 
each area belongs to a land-cover \emph{class} or \emph{type}.
Suppose that there are two land-cover maps of different scales 
that cover the same spatial region.
We consider the problem of finding a sequence 
of small incremental changes that gradually transforms 
the larger-scale map (the \emph{start map}) to 
the smaller-scale map (the \emph{goal map}).
We use this sequence to generate and show land-cover maps at 
intermediate scales (see \fig\ref{fig:AreaAgg_example}).
In this way, we try to avoid large and discrete changes
during zooming.

@@

With the same motivation, 
a strategy of hierarchical schemes has been proposed.
This strategy generalizes a more-detailed representation 
to obtain a less-detailed representation 
based on small incremental changes, 
e.g., the Generalized Area Partitioning tree (GAP-tree).
That tree can be constructed if only the larger-scale map is given
\citep{vanOosterom2005} 
or if both the larger-scale map and the smaller-scale map 
are given \citep{HaunertDilo2009}.
Typically, the next change in such a sequence 
is determined locally, in a greedy fashion.  
If we insist on finding a sequence that is optimal 
according to some global measures,
the problem becomes complicated.

We assume that there exist many-to-one relationships 
between the areas of the start map and the areas of the goal map.
This assumption is based on the fact that many algorithms 
\parencite[e.g.,][]{HaunertWolff2010AreaAgg,
vanSmaalen2003,Oehrlein2017Aggregation}
result in many-to-one relationships
when aggregating land-cover areas.
Their inputs and generalized results together
can be used as our inputs.
However, we should not use those algorithms
to generate a sequence of maps at different scales
because those algorithms do not take into account 
the consistency between the generated maps.
We use both a start map and a goal map instead of using only the start map
because our generated maps at intermediate scales should be able to
benefit from a goal map with high quality.

We term the areas of the goal map \emph{regions}.
That is, every region is the union of a set of areas 
on the start map.
The type of a region may differ from the types of its components. 
For example, a small water area together with 
multiple adjacent forest areas may constitute 
a large forest region on the \mine{goal} map.
However, we assume that every region, on the goal map, 
contains at least one area of the same type on the start map.
Our assumptions hold if the goal map has been produced 
with an automatic method for area aggregation, 
for example, by the method of \citet{HaunertWolff2010AreaAgg}.
That method used a land-cover map at a larger scale as input and 
produced a land-cover map at a single smaller scale.
Although \textcite{HaunertWolff2010AreaAgg}
attained results of high quality, 
they did not produce a sequence of maps.

Our method can also be extended to find an aggregation sequence 
for two maps (a start map and a goal map) that are from different sources.
In that case, one could compute a map overlay of the two maps
and use the result 
(with combined boundaries from both input maps and 
with land-cover classes 
from the given larger-scale map) 
as the start map.

In this paper, we try to find an optimal sequence
to aggregate the land-cover areas on the start map
one by one until we arrive at the goal map.
We first independently deal with each region of the goal map 
(with its components on the start map).
Once we have found an aggregation sequence for each region, 
we integrate all the sequences into an overall sequence,
which transforms the start map into the goal map
(see \fig\ref{fig:AreaAgg_IntegrateSequence}). 
Our aggregation sequence may be incorporated into
the GAP-face tree \citep{vanOosterom2005},
the map cube model \citep{Timpf1998},
or ScaleMaster \citep{Brewer2007Guidelines,Touya2013ScaleMaster}, 
to support on-the-fly visualization.
Smoothly (dis-)appearing areas can be realized
by integrating our results into the \emph{space-scale cube}
\parencite{vanOosterom2014Support,vanOosterom2014tGAPSSC}.

\begin{figure*}[tb]
\centering
\includegraphics[page=2]{AreaAgg_Preliminaries}
\caption{Integrating two aggregation sequences 
	of different regions: 
	the resultant sequence contains the given sequences 
	as subsequences and 
	always takes the subdivision with the smallest patch next.
	The gray arrows show the integration of the two regions.
}
\label{fig:AreaAgg_IntegrateSequence}
\end{figure*}

\mypar{Contribution}
We \mine{first} show \mine{some} related work (\sect\ref{sec:AreaAgg_RelatedWork}).
Then, we model our problem, present some basic concepts,
analyze the size of our model in a worst-case scenario,
and introduce our methods
(\sect\ref{sec:AreaAgg_Preliminaries}).
We define our cost functions 
(\sect\ref{sec:AreaAgg_CostFunctions}).
We prove that our problem is NP-hard
(\sect\ref{sec:AreaAgg_NP-hardness}).
Then, we develop and compare three methods 
for finding aggregation sequences.
First, we present 
a greedy algorithm (\sect\ref{sec:AreaAgg_Greedy}).
Second, we develop a new global optimization approach
based on the \Astar algorithm 
(\sect\ref{sec:AreaAgg_AStar}).
Third, we model our pathfinding problem as
an \emph{integer linear program} (ILP), 
and we solve this ILP with minimizing our cost function
(\sect\ref{sec:AreaAgg_ILP}).
Our ILP uses binary (0--1) variables. 
These variables help us to model our problem, 
but in general, it is NP-hard 
to solve an ILP optimally.
By comparing with the greedy algorithm, 
which is used as a benchmark,
we are able to see whether \Astar or the ILP-based algorithm, 
which are more complex and slower, indeed perform better.  
Our case study 
uses a dataset of the German topographic database ATKIS 
(\sect\ref{sec:AreaAgg_CaseStudy}).
In the concluding remarks, we show possible ways to improve our 
methods (\sect\ref{sec:AreaAgg_Conclusions}).

We do not simplify polylines in this paper.
The simplification can be handled separately from the
aggregation of areas, for example, 
by using one method of 
\textcite{Douglas1973},
\textcite{Saalfeld1999},
or \textcite{Wu2004DP}.
Those methods can be used to set up 
the binary line generalisation tree (BLG-tree) of
\textcite{vanOosterom1995Development},
which is a hierarchical data structure that 
defines a gradual line simplification process.
\mine{Note that simplifying polylines will not speed up 
our three algorithms.
The reason is that we compute the areas of the polygons 
and the lengths of the boundaries in a preprocessing.
These values will be associated with
a graph representation of the dataset, 
where polygons are represented as vertices and 
a boundary separating two polygons (no matter how detailed it is) 
is represented with a single edge.
During computation, the three algorithms do not need to go through 
the vertices of the land-cover areas.
}

@@

\emph{Continuous map generalization} (CMG)
has received a lot of attention
from cartographers and computer scientists.
\Textcite{vanKreveld2001} proposed five gradual changes
to support the continuous zooming of maps, 
which are \emph{moving}, \emph{rotating}, \emph{morphing}, 
\emph{fading}, and \emph{appearing}. 
He suggested using these gradual changes 
to adapt discrete generalization operators for CMG.
\textcite{Sester2005_CG} suggested simplifying building
footprints based on small incremental steps 
to animate each step smoothly.
\textcite{Li2012Continuous} built hierarchies of road segments,
which they then used to omit road segments 
from lower levels of the hierarchy.
Moreover, they evaluated similarities 
between their results and existing maps.
\textcite{Peng2017Building} gradually grew
buildings to built-up areas by aggregating buildings 
whenever they became too close.
\textcite{Touya2017Progressive} progressively replaced
buildings with blocks. 
In addition, their method automatically inferred landmarks 
and put the landmarks on top of the blocks.
\textcite{Suba2016Road} continuously generalized road networks
which are represented as a set of areas.
Their method repeatedly finds the least-important area 
and then either merges it with an adjacent area 
or collapses it to a line segment.
\textcite{Danciger2009} investigated the growing of regions, 
while preserving topology, area ratios, and
relative positions.
The strategy of using two maps at different scales
to generate intermediate-scale maps has been studied in multiple
representations, e.g., with respect to the selection of roads or
rivers~\parencite{Peng2012River,Girres2014}. 
Actually, that strategy is the key idea of the
morphing-based methods for CMG.
In order to morph from one polyline to another polyline,
which respectively represent, say, roads on a larger-scale map 
and a smaller-scale map, we first need to compute 
corresponding points between them 
\parencite[e.g.,][]{Cecconi2003,Noellenburg2008,Chazal2010BallMap,
Deng2015,Li2017_Building,Li2017Annealing}.
Then morphing can be realized by interpolating a set of 
intermediate polylines.
% Among the methods of computing corresponding points,
\textcite{Noellenburg2008} computed an optimum
correspondence between two given polylines 
according to some cost functions.
While straight-line trajectories 
are often used for interpolation
\parencite[e.g.,][]{Cecconi2003,Deng2015},
\textcite{Whited2011BallMorph} considered four other alternatives, 
i.e., \emph{hat}, \emph{tangent}, \emph{circular}, 
and \emph{parabolic} paths
based on so-called \emph{ball-map}
\parencite{Chazal2010BallMap}.
\textcite{Peng2016Admin} morphed county boundaries
to provincial boundaries.
For county boundaries that do not have corresponding 
provincial boundaries, they generated the correspondences based 
on \emph{compatible triangulations}.
\Textcite{vanOosterom2014Support} used
a data structure called
\emph{smooth topological generalized area partitioning}
to support visualizing CMG.
One of their contributions is that
a polygon merges another polygon continuously
by expanding over the latter.
\textcite{Huang2017Matrix} proposed a matrix-based structure 
to support CMG,
using a river network as an example.
For a given scale, 
their structure yields the rivers that should be kept 
as well as how much these rivers should be simplified.

@@

Map generalization generally specifies 
and takes into account requirements
in order to produce maps of high quality
\parencite{Stoter2009Requirements}.
We categorize requirements as hard and soft constraints.
For example,
when we aggregate a land-cover area into another, 
the type of the former is changed to the type of the latter. 
In this problem, a hard constraint could be that 
we aggregate only two areas at each step 
in order to keep changes small
(see for example \fig\ref{fig:AreaAgg_example}). 
A soft constraint could be that 
we wish to minimize the changes of types, e.g., 
we prefer aggregating a grass area into a farm area 
rather than into a settlement area.
This is a typical \emph{optimization} problem,
where we stick to hard constraints and 
try to fulfill soft ones as well as possible.
Optimization for map generalization is important 
not only because it finds optimal solutions,
but also because it helps us evaluate the quality of a model
\parencite{Haunert2017Label,
Haunert2008Assuring,Haunert2016Optimization}.
When we wish to minimize the changes of types
in aggregating areas one by one,
a model could be to minimize 
the \emph{greatest} change over all the steps.
Using a greedy algorithm,
we can minimize the change at each step,
but the result does not necessarily minimize the greatest change
over all the steps.
If a result is bad,
we cannot tell if the bad result comes from the model 
or from the greedy algorithm.
Using optimization,
we are able to find optimal solutions
of the model at least for small instances.
If even an optimal solution is bad,
then we can exclude that the bad result 
is from the greedy algorithm.
That is to say,
the bad result is because of the model.
In this case, we should improve the model; 
we may want to minimize 
the \emph{average} change over all the steps.
Moreover, optimization is useful for evaluating heuristics.
We need heuristics because
many optimization problems cannot be solved efficiently
\parencite[e.g.,][]{HaunertWolff2010AreaAgg,Haunert2016Partition}.
While heuristics can find some solutions in reasonable time,
it is important to know the quality of 
these solutions.
Fortunately, we can often find an optimal solution when 
the size of an instance is sufficiently small.
Consequently, we are able to evaluate 
the quality of a heuristic 
by comparing its results with optimal solutions
on small instances.

Optimization has been widely used in map generalization.
For example, \textcite{Harrie1999} displaced objects 
based on least-squares adjustments (LSA)
to solve spatial conflicts.
In his problem, the soft constraints 
for shapes and locations may contradict each other.
Therefore, it is necessary 
to mediate between these constraints, 
which can be done by LSA.
\textcite{Sester2005Optimization} used LSA not only for 
displacing objects but also for simplifying buildings. 
She required that 
the output boundaries should be 
as close to the original buildings as possible.
\textcite{Tong2015AreaLSA} generalized land-cover areas,
where LSA was used to preserve the sizes of 
the land-cover areas.
\textcite{Regnauld2001} grouped buildings based on 
minimum spanning trees in order to typify
the buildings in a group.
\textcite{Burghardt2005Snakes} smoothed lines based on 
energy minimization. 
According to his setting, a line contains less energy
if it is smooth and close to the original line.
He repeatedly displaced the line 
until a stable state 
in terms of minimizing his energy function is found.
\textcite{HaunertWolff2010AreaAgg} aggregated land-cover areas
based on mixed-integer linear programming
to generate a map at a target scale.
Their method is based on a global optimization.
They minimize a combination of type changes and cost for non-compact shapes 
while satisfying constraints on the sizes of the output regions.
\textcite{Haunertwolff2010Building} simplified building
footprints by solving an integer linear program (ILP).
They aimed at minimizing the number of edges in the output 
under the restriction that 
the simplified buildings must be topologically safe,
that is, the selected and extended edges must not intersect with 
each other.
\textcite{Oehrlein2017Aggregation} aggregated the departments 
of France according to unemployment rates based on integer 
linear programming; they used a cutting-plane method to 
speed up solving their ILP.
\textcite{Funke2017Simplification} simplified 
administrative boundaries based on an ILP.
Their aim was to minimize the number of edges
while keeping the resultant boundaries close to the original ones
and avoiding any intersection. 
At the same time, they required that every city, 
represented by a point, 
stays in the same face as before the generalization.

@@

Optimization becomes more delicate
when we deal with CMG.
In this field, there are requirements 
not only for a specific map
but also for relations between maps at difference scales. 
%
Some optimization techniques have been applied to CMG.
In the aforementioned article,
\textcite{Noellenburg2008} used dynamic programming
to match points of two polylines to support morphing
according to some matching costs.
\textcite{sahw-oarps-ICAGW13} used 
mixed-integer linear programming 
to select points of interest.
They required that a point, once disappeared, 
should not show up again during zooming out. 
They also required that any two points should be 
sufficiently far away from each other.
Based on these requirements, 
they wanted to show as many points as possible 
for a given scale interval.
\textcite{Chimani2014Eat} computed a deletion sequence
for a road network by integer linear programming
and efficient approximation algorithms.
They wanted to delete a stroke, 
which is a sequence of edges, at each step
while keeping the remaining network connected.
They assigned each edge a weight, 
and their objective was to maximize the total weight 
over all the road networks of all the steps.
\textcite{Peng2013LSA} defined trajectories 
based on LSA for morphing between polylines.
Their method required both angles in vertices and edge lengths
change linearly.
As those requirements may not agree with each other,
their method mediates between them using LSA.

@@

\end{proof}

@@

\section*{Data and codes availability statement}
